### 2021-09-29 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_betadiversity_response@3767f8dbef7c29829f310e04a5edeb5fb7ccffb5 🚀

\begin{figure}
\hypertarget{fig:conceptual}{%
\centering
\includegraphics{figures/betadiv_response_figure.png}
\caption{TK}\label{fig:conceptual}
}
\end{figure}

@@

Applying this framework to networks requires a few additional
definitions. Although ecologists tend to think of networks as their
adjacency matrix, this representation is far from optimal to get a solid
understanding of which elements should be counted as part of which set
when measuring network dissimilarity. For this reason, we need fall back
on the definition of a graph as a pair of sets, wherein
\(\mathcal{G} = (V, E)\). These two components \(V\) and \(E\) represent
vertices (nodes, species) and edges (interactions), where \(V\) is
specifically a set containing the vertices \(\mathcal{G}\), and \(E\) is
a set of ordered pairs, in which every pair is composed of two elements
of \(V\); an element \(\{i,j\}\) in \(E\) indicates that there is an
interaction \emph{from} species \(i\) to species \(j\) in the network
\(\mathcal{G}\).

>>>>

\begin{figure}
\hypertarget{fig:conceptual}{%
\centering
\includegraphics{figures/betadiv_response_figure.png}
\caption{The dissimilarity of two networks (green and orange) of equal
richness \(S\) (this also holds for unequal richness) depends on three
families of interactions: those that are unique because of species
turnover (in a pale color), those that are unique because of rewiring
(in a saturated color), and those that are shared (in black). Assuming
that the chance of sharing a species between the two networks is \(p\),
then there can be at most \(p^2\times S^2\) shared links -- for this
reason, overall network dissimilarity (\(\beta_{wn}\)) will have a
component tied to species turnover, which is
\(\beta_{st}\).}\label{fig:conceptual}
}
\end{figure}

@@

Applying this framework to networks requires a few additional
definitions. Although ecologists tend to think of networks as their
adjacency matrix (as is presented in fig.~\ref{fig:conceptual}), this
representation is not optimal to reach a robust understanding of which
elements should be counted as part of which set when measuring network
dissimilarity. For this reason, we need fall back on the definition of a
graph as a pair of sets, wherein \(\mathcal{G} = (V, E)\). These two
components \(V\) and \(E\) represent vertices (nodes, species) and edges
(interactions), where \(V\) is specifically a set containing the
vertices \(\mathcal{G}\), and \(E\) is a set of ordered pairs, in which
every pair is composed of two elements of \(V\); an element \(\{i,j\}\)
in \(E\) indicates that there is an interaction \emph{from} species
\(i\) to species \(j\) in the network \(\mathcal{G}\).
